Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-27 mr-review.Rmd
grapple text added

>>>>

@bowden_improving_2019

@wang_causal_2021 developed a framework, GRAPPLE, for performing two-sample MR with weak and strong 
instruments. Using GWAS summary statistics as inputs, GRAPPLE extends MR-RAPS and can detect presence of horizontally 
pleiotropic pathways, infer the causal direction, and perform multivariable MR. Central to the 
GRAPPLE framework is the observation that a horizontally pleiotropic pathway often gives rise to an 
additional mode in the profile likelihood. GRAPPLE uses the presence of multiple profile likelihood 
modes to diagnose horizontal pleiotropy with effects that are grouped by pathway. 
GRAPPLE facilitates identification of SNP instruments that contribute to the 
additional profile likelihood modes. A researcher using GRAPPLE may then recognize 
a confounding factor for each mode. With additional GWAS summary data with traits 
that reflect the confounding factors, GRAPPLE can fit multivariable MR models when
the InSIDE assumption holds for the remaining horizontally pleiotropic effects [@wang_causal_2021].
